{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-06 wacv_for_review.tex
Some more revision

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target {\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.} 
  {\it YoungWoo : In this paragraph, we mention two of the translation filters and then we say
  translation filter needs background whereas the scale filter does not.}
Figure \ref{fig:Filters} shows examples of three filters.

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail each part of the KCF.

@@

{\it YoungWoo : I placed EnKCF with traditional and deep features section right after EnKCF section. Later, you
placed them after the Kernelized Correlation Filter section. }

@@

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters} (b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noises the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$, for capturing a smaller area. This is
because the translation filter, {\it target + small background}, does
not contain much of the background area around the target. Figure
\ref{fig:Filters} (a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters} (c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
due to two major reasons: (1) zero padding size and (2) integration of color features.
This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. {\it Burak: Why do we need to keep the run-time complexity
  of $R_{S}$ and $R_{t}^{L}$ the same?} {\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$ to 
  have similar fps (30fps) to avoid missing frames on an embedded system. We can think of each one as an individual tracker
  and we do not want one operating at 10fps while others running at 30 fps.} By reducing the template size of $R_{s}$,
   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.

@@

As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$, where $w_{p}$
denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
We further improved the performance by employing deeper features in the scale filter since it has zero
padding around the target.

>>>>

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background bigger than that of the first filter, $R_{t}^{S}$, \textit{target}+\textit{large background}. 
We set up {\it E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target {\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.} 
  {\it YoungWoo : In this paragraph, we mention two of the translation filters and then we say
  translation filter needs background whereas the scale filter does not.}
Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the {\it E}nKC with hand-crafted features, dedicated to run
on low-end embedded systems, and deep features, designed to run on
the systems with GPUs. Later, we will briefly document the fundamental 
concepts of the KCF and Particle Filter, designed to smooth transitions 
between KCFs.

@@

{\it YoungWoo : I placed EnKCF with traditional and deep features section right after EnKCF section. Later, you
placed them after the Kernelized Correlation Filter section. To me, it makes more
sense to place them right after the EnKCF section.}

@@

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noise the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
does not contain much of the background area around the target. Figure
\ref{fig:Filters}(a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
and (2) integration of color features. This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. {\it Burak: Why do we need to keep the run-time complexity
  of $R_{S}$ and $R_{t}^{L}$ the same?} {\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$ to 
  have similar fps (30fps) to avoid missing frames on an embedded system. We can think of each one as an individual tracker
  and we do not want one operating at 10fps while others running at 30 fps.} By reducing the template size of $R_{s}$,
   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.

@@

As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. Then it uses the confidence maps of 
{\it E}nKCF as observation to update the state. The weight of a particle is computed as
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j), 
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
We further improved the performance by employing deeper features in the scale filter 
with zero padding around the target.
